### 2024-01-09 inst/scripts/exploreNeutralTraits.Rmd
merge stash

```{r runsimu,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=10000
quickV=modelVector(K=ki, m=1, b=0.2, r=0.01, rho=0, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150)
population=quickV$population
population[population[,"cid"]!= -1 ,"cid"] = as.numeric(as.factor(as.character(population[population[,"cid"]!= -1 ,"cid"])))
population[,"fid"] = as.numeric(as.factor(as.character(population[ ,"fid"])))
ids = as.numeric(as.factor(as.character(population[ ,"id"])))
names(ids)=population[,"id"]
population[,"id"] = as.numeric(as.factor(as.character(population[ ,"id"])))
population[,"partner"]=as.numeric(ids[as.character(population[,"partner"])])
population[is.na(population[,"partner"]),"partner"]=-1
initcomus$size=as.numeric(table(population[,"community"]))

@@

```{r,eval=F}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=2000
repli=50
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)

@@

@@

par(mfrow=c(2,3))
for(rr in 1:2){
for(pth in 1:3){
plot(1,1,ylim=c(0,1),xlim=c(0,1000),pch="n")
sapply(rhodepSBBIB[[rr]][[pth]],function(olo)sapply(1:4,function(tr)lines(olo[,tr],col=tr)))
}}
```

@@

>>>>

```{r runsimu,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=10000
quickV=modelVector(K=ki, m=1, b=0.2, r=0.01, rho=0, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150)
data(population)

@@

```{r,eval=F}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=5000
repli=10
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=ki,km=km,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)

initcomus$adaptivetraits[1,]=c(1,1,1)
cl <- makeCluster(10,type="FORK")

rhos=c(0,1)
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           #allposthoriz=replicate(repli,{
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL,beta=0)
                                      pop=quickV$population
                                      #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                      #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           #allprehoriz=replicate(repli,{
           allprehoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                     #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

@@

stopCluster(cl)
saveRDS(file="precompSBbibi_adc.RDS",rhodepSBBIB)
```

```{r,out.width="30%"}
rhodepSBBIB=readRDS("../inst/scripts/precompSBbibi.RDS")

@@

pdf("neutral_dynamic_distrib.pdf",width=12)
par(mfrow=c(2,3))
pathways= c("in-law","horiz before","horiz after")
for(rr in 1:2){
for(pth in 1:3){
plot(1,1,ylim=c(0,1),xlim=c(0,5000),type="n",xlab="time",ylab="freq",main=paste(pathways[pth],"rho=",rhos[rr]))
sapply(rhodepSBBIB[[rr]][[pth]],function(olo)sapply(1:4,function(tr)lines(olo[,tr],col=tr)))
}}
par(xpd=NA)
legend(x=-9,y=1.5,lwd=4,col=1:4,legend=paste0("t",1:4),cex=1,bty="n")
dev.off()

pdf("initial_distrib.pdf",width=7)
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
initcount=as.matrix(aggregate(population[,traitsid],by=list(population[,"community"]),sum)[,-1])
rownames(initcount)=LETTERS[1:4]
barplot(t(as.matrix(initcount)),beside=T,legend=T,xlab="community",args.legend=list(bty="n",title="traits",x="top"),ylim=c(0,180),ylab="#individual",col=1:4)
dev.off()

pdf("legend.pdf",width=5)
plot(1,1,type="n",ann=F,axes=F)
legend("center",fill=1:4,legend=paste0("t",1:4),cex=5)
dev.off()
```

@@

||||||| constructed merge base
=======
```{r}

sapply(rhodepSB[[rr]][[pth]],function(olo)sapply(1:4,function(tr)lines(olo[1000,tr],col=tr)))

apply(sapply(rhodepSB[[1]][[3]],function(i)i[5000,])==1,1,sum)
do.call("rbind",quickV$traitsumary)/quickV$popsize

tstep=10000
rhos=c(0,1)
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.2, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           #allposthoriz=replicate(repli,{
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL,beta=0)
                                      pop=quickV$population
                                      #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                      #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           #allprehoriz=replicate(repli,{
           allprehoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)
                                     #sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

stopCluster(cl)

```
```{r}
devtools::load_all(".")
z=4
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$post[,"i"]=1
neutraltraitsParam$s=c(0,1)
traitsid=paste0("t",1:z)
km=0
ki=z
G=2
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=3,km=1,n=3),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)
communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
data(population)
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=200
rhos=c(0,1)
repli=10
rhodepSBBIB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.02, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)
           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL,beta=0)
                                      pop=quickV$population
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           allprehoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)
           neutraltraitsParam$pre[,"h"]=0
           neutraltraitsParam$post[,"o"]=1
           allposthoriz=parSapply(cl,1:repli,function(r){
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.1, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     do.call("rbind",quickV$traitsumary)/quickV$popsize
                              },simplify=F)
           list(allinlaw=allinlaw,allposthoriz=allposthoriz,allprehoriz=allprehoriz)
}
)

stopCluster(cl)
```

attempt to do stuff:

```{r}

rhodep=readRDS("../precompSB_3rho.RDS")
rangeZ=range(unlist(rhodep))
pdf("neutral_final_distrib.pdf",width=9)
par(mfrow=c(3,3),xpd=F)
par(oma=c(5,5,5,1))
par(mar=c(1,3,0,0))
allmatrices=lapply(rhodep,lapply,matmean)

lapply(allmatrices,lapply,image,zlim=rangeZ,xlab="",x=c(1,2,3,4),y=c(1,2,3,4),ylab="traits",xaxt="n")
axis(1,label=LETTERS[1:4],at=1:4)
mtext(c("in-law","horiz beforw","horiz after"),3,2,at=c(0.2,.5,.85),outer=T)
mtext("community",1,2)
mtext("rho",2,4,outer=T,cex=.8)
mtext(c("0",".5","1"),2,1,5,at=c(0.3,.6,.9),outer=T,cex=.9)
mtext("traits",2,0,at=0.2,outer=T,cex=.8)
dev.off()
```
